Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-19 WSSSPE3/report/wg_main_software_credit.tex
undoing an edit

A number of groups external to WSSSPE (although with some overlapping members)
also focused on aspects of software credit, including the FORCE11 Software
Citation Working Group (see plans for coordination below). In addition, a
Software Credit workshop\footnote{London Software Credit workshop:
\url{http://www.software.ac.uk/software-credit}} convened in London on October
19, following the conclusion of WSSSPE3. See
Appendix~\ref{sec:appendix_SW_credit} for more detailed discussion of related
activities.

>>>>

A number of groups external to WSSSPE (although with some overlapping members)
are also focused on aspects of software credit, including the FORCE11 Software
Citation Working Group (see plans for coordination below). In addition, a
Software Credit workshop\footnote{London Software Credit workshop:
\url{http://www.software.ac.uk/software-credit}} convened in London on October
19, following the conclusion of WSSSPE3. See
Appendix~\ref{sec:appendix_SW_credit} for more detailed discussion of related
activities.
